Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-06-25 doc/manuscript/ESSDmanuscript.Rmd
update table 2
I believe all the info is now complete/ correct, but some formatting is required

```{r table_ForCfieldmapping, eval = TRUE, echo=FALSE, warning=FALSE}

@@

library(knitr)
library(kableExtra)
knitr::kable(ForC_variables_included, format = "latex",
             longtable = TRUE,
             caption = "\\textbf{Mapping of ForC fields to EFDB.}") %>%
  kableExtra::kable_styling(full_width = TRUE, latex_options = c("repeat_header")) %>%
  row_spec(0, bold = TRUE)
```

>>>>

\clearpage
```{r table_ForCfieldmapping, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)

@@

knitr::kable(ForC_variables_included, format = "latex",
             longtable = TRUE,
             caption = "\\textbf{Mapping of ForC fields to EFDB.} See footnotes at end of table (still need to be properly inserted). ") %>%
  row_spec(0, bold = TRUE) %>%
kableExtra::kable_styling(full_width = TRUE, latex_options = c("repeat_header", "hold position"))

```
'Required' field indicates whether the field is required by EFDB: yes = value required; (yes) = input required, missing value acceptable if not reported; auto = present within ForC infrasructure, and therefore will always be exported to EFDB ; (no) = not required for EFDB, but required for ForC and therefore will always be exported to EFDB; no = not required, but exported to EFDB when a value is present.

** '(yes)' for most recent severe disturbance; 'no' for other history events

### 2021-06-25 doc/manuscript/ESSDmanuscript.tex
update table 2
I believe all the info is now complete/ correct, but some formatting is required

@@

\caption{\label{tab:table_ForCfieldmapping}\textbf{Mapping of ForC fields to EFDB.}}\\

@@

\textbf{ForC table} & \textbf{ForC field} & \textbf{EFDB field} & \textbf{Use} & \textbf{Required}\\

@@

\caption[]{\textbf{Mapping of ForC fields to EFDB.} \textit{(continued)}}\\

@@

 & soil.texture, sand, silt, clay, soil.classification, FAO.ecozone & Parameters/ Conditions & direct mapping & no\\

@@

 & country, state, city, lat, lon, masl, continent, Koeppen, mat, map & Region/Regional conditions & direct mapping, and lat-lon used to extract continent, Koeppen, and FAO.ecozone & no\\

@@

History & date, hist.cat, hist.type & 1996 Source/Sink Categories, 2006 Source/Sink Categories, Abatement/Control technologies & used to determine distmrs.type for Source/Sink Categories, generate list of events for Abatement/Control technologies & (yes)\\

@@

>>>>

\clearpage

@@

\caption{\label{tab:table_ForCfieldmapping}\textbf{Mapping of ForC fields to EFDB.} See footnotes at end of table (still need to be properly inserted). }\\

@@

\textbf{ForC table} & \textbf{ForC field} & \textbf{EFDB field} & \textbf{Usage} & \textbf{Required}\\

@@

\caption[]{\textbf{Mapping of ForC fields to EFDB.} See footnotes at end of table (still need to be properly inserted).  \textit{(continued)}}\\

@@

 & lat, lon & Region/Regional conditions & direct mapping; used to extract continent, Koeppen, and FAO.ecozone & (no)\\

@@

 & country, state, city, masl,  mat, map & Region/Regional conditions & direct mapping & no\\

@@

 & continent, Koeppen & Region/Regional conditions & direct mapping & auto\\
 & soil.texture, sand, silt, clay, soil.classification & Parameters/ Conditions & direct mapping & no\\
 & FAO.ecozone & Parameters/ Conditions & direct mapping & auto\\
History & date, hist.cat, hist.type & 1996 Source/Sink Categories, 2006 Source/Sink Categories, Abatement/Control technologies & used to determine distmrs.type for Source/Sink Categories, generate list of events for Abatement/Control technologies & (yes)/no**\\

@@

`Required' field indicates whether the field is required by EFDB: yes =
value required; (yes) = input required, missing value acceptable if not
reported; auto = present within ForC infrasructure, and therefore will
always be exported to EFDB ; (no) = not required for EFDB, but required
for ForC and therefore will always be exported to EFDB; no = not
required, but exported to EFDB when a value is present.

** `(yes)' for most recent severe disturbance; `no' for other history
events
